Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2023-05-08 src/tex/ms.tex
[showyourwork] overleaf sync

    \begin{figure}
        \script{patches.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/patches.pdf}
            \caption{
                Grid of overlapping patches of size 8x8 pixels. The overlap size was chosen to be 2 pixels.
            }
            \label{fig:patches}
        \end{centering}
    \end{figure}

@@

    To normalise the patches \cite{Zoran2011} proposed to subtract the patch mean before learning the GMM. This leads to the GMM modeling the same morphological features at different levels of contrast as different components. While this proved to be beneficial in the context of reconstructing natural images it does not scale to images with high dynamic range, only at the cost of introducing a lot more components to the GMM, which is unfeasible in practice due to limited availability of training data and computational resources. For this reason we propose the following modified normalisation for the patches:
    %
    \begin{equation}
        \label{eq:patch-norm}
        \tilde{\mathbf{x}}_n = \frac{\mathbf{x}_n - \Bar{\mathbf{x}}_n}{\Bar{\mathbf{x}}_n}
    \end{equation}

>>>>

    \begin{figure}
        \script{patches.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/patches.pdf}
            \caption{
                Grid of overlapping quadratic patches of size $8\times8$ pixels on top of an example image of the size $128 \times 68$ pixels. The overlap size was chosen to be $2$ pixels, which results in 50 patches in total. The patches are shown translucent, such that the light \enquote{stripes} result from two neighboring overlapping patches, while the small, even lighter, squares result from four patches overlapping at the their corners.
            }
            \label{fig:patches}
        \end{centering}
    \end{figure}

@@

    To normalise the patches \cite{Zoran2011} proposed to subtract the patch mean before learning the GMM. This leads to the GMM modeling the same morphological features at different levels of contrast as different components. While this proved to be beneficial in the context of reconstructing natural images it does not scale to images with high dynamic range. Only at the cost of introducing a lot more components to the GMM, which is unfeasible in practice due to limited availability of training data and computational resources. For this reason we propose the following modified normalisation for the patches:
    %
    \begin{equation}
        \label{eq:patch-norm}
        \tilde{\mathbf{x}}_n = \frac{\mathbf{x}_n - \Bar{\mathbf{x}}_n}{\Bar{\mathbf{x}}_n}
    \end{equation}
